Kindly Bent to Free Us

### 2020-06-02 kindly/infer/infer.tex
Present the properties required on the constraint system.

\subsection{Constraint Solving}
\label{infer:solving}

@@

For concision, we demonstrate the constraint solving
algorithm with an example. The complete constraint system is
defined in \cref{appendix:constraints}.
%
\input{infer/exampleconstr}

Our algorithm respect the properties
of \hmx, computes principal normal forms
and simplifies constraints significantly.
All the simplification mechanisms presented
here, including the variance-based one, are complete.
It is also possible to add ``best-effort'' simplification
rules which help reduce the size of inferred signatures even further
\citep{DBLP:conf/aplas/Simonet03}.

%
% We now show that this algorithm is well-behaved with respect to entailment
% and computes unique normal forms.

% \begin{property}[Principal normal form]
%   Normalization computes principal normal forms for $\CL$, i.e.
%   given a constraint $D\in\CL$, a substitution $\phi$ and
%   $(C,\unif) = \normalize{D}{\phi}$,
%   then $\phi\leq\unif$,
%   $C \equivC \unif D$ and
%   $\unif C = C$.
% \end{property}

% \begin{property}[Principal constraints]
%   $\CL$ has the principal constraint property, i.e.
%   for every $D\in\CL$, and a substitution $\unif$,
%   either $D$ does not have a normal form, or it has
%   a principal normal form.
% \end{property}

% \begin{property}[Regular constraint system]
%   $\CL$ is regular, ie, for $x, x'$ two types or kinds,
%   $\entail{}{\Ceq{x}{x'}}$ implies
%   $\fv{x} = \fv{x'}$
% \end{property}

% The proofs are given in \cref{appendix:constraints}. These three properties
% are sufficient to state that $HM(\CL)$ provides principal type inference.
% However, we use an extension of \hmx with kind inference
% and affine types and borrows.
% We now show that \hmx's completeness and soundness theorems are still valid on
% this extended system.

>>>>

\subsection{Constraints}
\label{infer:solving}

@@

To properly define our type system, we need to define $\CL$, a constraint
system equipped with an entailment relation noted $\operatorname{\vdash_e}$
and a normalizing function.
For concision, we first demonstrate the constraint solving
algorithm with an example. We then state the various properties
that make it suitable for use in the \hmx framework.
The complete constraint system is
defined in \cref{appendix:constraints}.

\subsubsection{Constraints normalization by example}

\input{infer/exampleconstr}

\subsubsection{Properties of the constraint system}

To apply \hmx to $\CL$, normalize must compute principal normal forms
and $\CL$ must be regular.

\begin{property}[Principal normal form]
  Normalization computes principal normal forms for $\CL$, i.e.
  given a constraint $D\in\CL$, a substitution $\phi$ and
  $(C,\unif) = \normalize{D}{\phi}$,
  then $\phi\leq\unif$,
  $C \equivC \unif D$ and
  $\unif C = C$.
\end{property}

\begin{property}[Regular constraint system]
  $\CL$ is regular, ie, for $x, x'$ two types or kinds,
  $\entail{}{\Ceq{x}{x'}}$ implies
  $\fv{x} = \fv{x'}$
\end{property}

These properties
are sufficient to state that $HM(\CL)$ provides principal type inference.
The next section states that this properties carries over to our extension
of \hmx
with kind inference, affine types and borrows.
%
This algorithm also simplifies constraints significantly.
All the simplification mechanisms presented
here, including the variance-based one, are complete.
It is also possible to add ``best-effort'' simplification
rules which help reduce the size of inferred signatures even further
\citep{DBLP:conf/aplas/Simonet03}.
